On finiteness of structures produced deterministically by oritatami co-transcriptional folding \thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779}

### 2018-11-08 paper.tex
Preliminaries writing started
I have just added a file "uos_preliminaries", which includes the tex
source for preliminaries. I will work on it so that please do not touch
it without any permission from me.
Title, Author, Institute
I added my name and institute. Please add your info by yourself.

\title{On finiteness of structures produced deterministically by co-transcriptional folding}
\author{}
\date{}

@@

@@

\section{Preliminary}

>>>>

\title{On finiteness of structures produced deterministically by oritatami co-transcriptional folding
\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779}
}
\author{Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
\institute{Akita University 
\and
University of Electro-Communications, 1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan
}

@@

\begin{abstract}

\end{abstract}

@@

\section{Preliminaries}
\input{uos_preliminaries.tex}
